---
title       : MtCars Prediction Tool
subtitle    : 
author      : cjstev
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
mode        : selfcontained # {standalone, draft}
---

## Introduction and Inspiration

How many times have you been laying in bed wishing that you had a tool that could dynamically predict mpg from the mtcars dataset with a simple linear regression!?  Well now, you can.


--- 

## What is mtcars?

<iframe src = 'https://stat.ethz.ch/R-manual/R-devel/library/datasets/html/mtcars.html' height = '600px'></iframe>

--- 

## Plotting Mtcars

```{r, echo=FALSE,fig.width=14, fig.height=4}
require(ggplot2); data(mtcars)
p1<-qplot(wt,mpg,data=mtcars,col=cyl,main="Wt vs MPG")
p2<-qplot(hp,mpg,data=mtcars,col=cyl,main="Hp vs MPG")
p3<-qplot(qsec,mpg,data=mtcars,col=cyl,main="1/4 mi Time vs MPG")
p4<-qplot(carb,mpg,data=mtcars,col=cyl,main="# of Carbs vs MPG")
grid.arrange(p1,p2,p3,ncol=3)
```

- Here we see that a few of the metrics appear to be correlated to MPG of the cars in the dataset.  
- Unfortunately, we don't know how well correlated the data is and we can't predict outside of the sample (yet!).


---
## Methodolgoy

- Utilizing widgets in shiny, the app allows the user to actively select the predictor from the mtcars dataset.
- Next the app fits a linear regression with the lm() function.
- Finally, the app allows the user to select an input value and predict the mpg.

```{r,echo=FALSE,fig.width=7, fig.height=4,fig.align='center'}
data(mtcars)
mtcars$type<-"Original"
mtcars<-subset(mtcars,select=c(hp,mpg,type))
newx<-150.0
fit<-lm(mpg~hp,data=mtcars)
newy<-predict(fit,newdata=data.frame(hp=newx))
newdata<-rbind(mtcars,data.frame(hp=newx,mpg=newy,type="New"))
p<-qplot(hp,mpg,data=newdata,main='Prediction of mpg using mtcars',xlab='hp',ylab='mpg',color=type)
p+geom_abline(intercept=fit$coefficients[1],slope=fit$coefficients[2],color='#0000ff22',size=1.1)
print("At 150 hp, your car will use 19.864 mpg")
```




--- .class #id 

## Link to Project


<iframe src = 'https://cjstev.shinyapps.io/ShinyProject/' height = '600px'></iframe>

